---
title: "Project 3 Supervised Learning"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

Initial setup (add cleaning / tidying if necessary)

```{r}
library(randomForest)
library(rpart)
library(partykit)
library(caret)
sal <- read.csv("/cloud/project/Salaries.csv") 
sal<- na.omit(sal)
```
Split data into training and test data.

```{r}
set.seed(8675309) 
train_index <- createDataPartition(sal$salary, p=.9, list = FALSE)   # caret functions

  train_data <- sal[train_index,]   # Training Data
   test_data <- sal[-train_index,]  # Test Data
```

**CART**

```{r}
set.seed(8675309) 
salary.ct <- rpart (salary ~ ., data = train_data)
salary.ct.party <- as.party(salary.ct)
plot (salary.ct.party)
```
Generate predictions for our hold-out testing data and compare to actual with a plot and correlation

```{r}
predictions.ct <- predict(salary.ct, test_data)
plot(predictions.ct,test_data$salary)    # compare to actual value
cor(predictions.ct,test_data$salary)
```

**Bagging**
```{r}
   set.seed(8675309)
   salary.bg <- randomForest(salary ~ ., data=train_data, mtry=ncol(sal)-1, importance=TRUE, na.action=na.omit)
   print(salary.bg)
   round(importance(salary.bg), 2)   # Variable Importance
   varImpPlot(salary.bg)
```
Generate predictions for our hold-out testing data and compare to actual with a plot and correlation

```{r}
predictions.bg <- predict(salary.bg, test_data)
plot(predictions.bg,test_data$salary)    # compare to actual value
cor(predictions.bg,test_data$salary)
```

**Random Forest**
Note: Default values of mtry = sqrt(p) Classification
                             = p/3     Regression
where p is number of explanatory variables
```{r}
   set.seed(8675309)
   salary.rf <- randomForest(salary ~ ., data=train_data, mtry=3, importance=TRUE, na.action=na.omit)
   print(salary.rf)
   round(importance(salary.rf), 2)   # Variable Importance
   varImpPlot(salary.rf)
```
Generate predictions for our hold-out testing data and compare to actual with a plot and correlation

```{r}
predictions.rf <- predict(salary.rf, test_data)
plot(predictions.rf,test_data$salary)    # compare to actual value
cor(predictions.rf,test_data$salary)
```





